%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author:
% Andres Solis Montero, Fall 2015
% CV styled document based on scrartcl class.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{cv}
\begin{document}
\pagenumbering{gobble}
\begin{cv}{\HeaderName{Andr\'es Sol\'is Montero}}
\info{\href{http://www.solism.ca}{www.solism.ca}}
	 {(613) 265-4482}
	 {\href{mailto:andres@solism.ca}{andres@solism.ca}}
	 {1739 Sunview Dr.}
	 {Ottawa ON}
	 {Canada K1C 5B3}

\NewHeader{Overview}

\desc{}{\textbf{Professional Summary}}{A creative leader and senior data scientist with a Ph.D. in Computer Science, specializing in Computer Vision, Image Processing, Machine Learning and Deep Learning solutions with a solid mathematical, data management, and analytics background. Published author with over 1000 citations and technical reviewer for over nine years. My experience brings invaluable insight into analyzing, processing, and reporting meaningful reports and decisions and visualizing data. I am a versatile researcher with a broad knowledge of programming languages, databases, and data structures. I have taught courses in computer science, programming languages, and advanced programming concepts for over ten years at the University Level. }
\desc{}{\textbf{Management / Team Lead}}{Over eight years of management experience and team leader who performs and delegates multiple duties while motivating staff, making sound decisions, and working with managers and staff at all levels of responsibility. Excellent communication skills with a creative mindset. I like encouraging collaborative work environments, stimulating group creativity and promoting knowledge sharing. I have extensive experience delivering technology products from conception to delivery while allocating resources and timelines successfully. 
 }
 

\desc{}{\textbf{Full-Stack Software Developer \&  Applied AI \& DevOps}}{Over 15+ years of experience as a full-stack software developer with vast experience in Cyber Security, DevOps, and Cloud Native Solutions. A developer who enjoys simplicity in creative design code with a creative eye for UX and UI design. I am a seasoned programmer with experience in multiple programming paradigms, data structures and algorithms. I have architected, led, and deployed various AI Cloud solutions and products from conception to delivery. I specialized in Computer Vision, Machine Learning, Deep Learning, CNN, Business Analytics, and Information Extraction. I have deployed products with the following tech stack: Python, C++, Java, Web technologies, OAuth, SQL and NoSQL databases, Azure Cloud, Kubernetes, and Containerization (i.e., Docker).}

 \newpage 
\NewHeader{Work Experience}


\desc{\href{http://www.statcan.gc.ca/}{DScD, StatCan, Canada}}{2020--Present}{\textbf{Lead Data Scientist }\\ 
   Technical Lead of several projects under the Data Science Division / Product Delivery Section for clients such as Public Health Agency of Canada (PHAC), Health Canada (HC), and Statistics Canada (StatCan). Working on product delivery, architecture, production planning, pipelines, data integration, ML modelling, deep learning, and cloud integration (i.e., Kubernetes and Microsoft Azure) for the following projects: Cyclops, COVID-19 PPE - EPI Model, Frontier Counts, SEDAR, and Hydra.  \\
%\textbf{Reference}: Robert Johnsen \ $\cdotp$\ \ +1 (201) 424-6374 \ \ $\cdotp$\ \ \href{mailto:robertj@tempo-analytics.com}{robertj@tempo-analytics.com} \\
%\textbf{Reference}: Prof.~Robert Lagani\`ere \ $\cdotp$\ +1 (613) 562-5800x6707\ $\cdotp$\ \href{mailto:robert@laganiere.name}{robert@laganiere.name} 
}

\desc{\href{http://tempo-analytics.com/}{Tempo Analytics, Canada}}{2016--Present}{\textbf{Co-founder, CTO \& Project Manager, Research \& Development}\\ 
   Architect, team technical lead in charge of developing a server-client cloud application to deliver the speed of service time statistics for the Quick Service Industry. In charge of conceptualizing and building novel computer vision products using machine learning and deep learning neural networks for customer detection, people re-identification, and metric learning. Allocating resources, tasks and defining timelines and milestones while communicating results to our stockholders and clients. Manage a team of software engineers, Master, and Ph.D. candidates to build the right solutions for our product. Systematically generating progress reports and analytics tools to produce business intelligence for stakeholders and clients.\\
%\textbf{Reference}: Robert Johnsen \ $\cdotp$\ \ +1 (201) 424-6374 \ \ $\cdotp$\ \ \href{mailto:robertj@tempo-analytics.com}{robertj@tempo-analytics.com} \\
%\textbf{Reference}: Prof.~Robert Lagani\`ere \ $\cdotp$\ +1 (613) 562-5800x6707\ $\cdotp$\ \href{mailto:robert@laganiere.name}{robert@laganiere.name} 
}

\desc{\href{http://www.eecs.uottawa.ca/}{University of Ottawa, Canada}}{2010--2016}{\textbf{Research Assistant, Computer Vision Software Developer}\\ 
   Responsible for writing research papers, presenting research findings, and develop computer vision and machine learning software to test and validate the results. Research on shape analysis, object detection and tracking solutions for augmented reality, robot localization, and surveillance applications. \\
%\textbf{Reference}: Prof.~Jochen Lang \ $\cdotp$\ \ +1 (613) 562-5800x6317\ \ $\cdotp$\ \ \href{mailto:jlang@eecs.uottawa.ca}{jlang@eecs.uottawa.ca}\\
%\textbf{Reference}: Prof.~Robert Lagani\`ere \ $\cdotp$\ +1 (613) 562-5800x6707\ $\cdotp$\ \href{mailto:robert@laganiere.name}{robert@laganiere.name} 
}

%\desc{\href{http://www.eecs.uottawa.ca/}{University of Ottawa, Canada}}{2008--Present}{\textbf{Teacher Assistant}\\ 
 % Over 10 courses in the field of Computer Science and Programming Languages. See Teaching Experience section for details. }


%\desc{\href{http://www.eecs.uottawa.ca/}{Habitat 7}}{2014--2015}{\textbf{Research and Software Developer} (Connect Canada Internship)\\ Research and develop 3D object detection algorithms for augmented reality applications\\ \textbf{Reference}: Jochen Lang \ $\cdotp$\ \ +1 (613) 562-5800x6317\ \ $\cdotp$\ \ \href{mailto:jlang@eecs.uottawa.ca}{jlang@eecs.uottawa.ca}\\
%\textbf{Reference}:  Robert Lagani\`ere\ +1 (613) 562-5800x6707\ \ $\cdotp$\ \ \href{mailto:laganier@eecs.uottawa.ca}{laganier@eecs.uottawa.ca}}%

%\Description{\MarginTextYear{\href{http://www.eecs.uottawa.ca/}{University of Ottawa, Canada}}{2011--2012}Work study program. Development and design of a MVC web platform (PHP and jQuery) for the faculty of Health Sciences.  \\ \textbf{Reference}: Guy Czaika \ +1 (613) 562 5800x8651\ \ $\cdotp$\ \ \href{mailto:gczaika@uottawa.ca}{gczaika@uottawa.ca}}
%\NewEntry{2011--2012}{Senior Web Programmer, \textsc{Canada}}

\desc{\href{http://www.proximify.ca/}{Proximify}}{2011--2012}{\textbf{Senior Web Developer}\\Design and development of a javascript engine powering UniWeb and CCV Sync. Proximify is a cloud-based software for academic institutions and grant agencies. Envisioning and building a research network tool for creating and maintaining your Canadian Common CVs.  \\ %\textbf{Reference}: PhD. Diego Macrini \ +1 (613) 828 6274\ \ $\cdotp$\ \ \href{mailto:macrini@proximify.ca}{macrini@proximify.ca}%
}


\desc{\href{http://dalendesign.com/}{Dalen Design}}{2010--2011}{\textbf{Web Developer} \\ Development and maintenance of the e-commerce website: \href{http://www.hottubcoverscanada.ca/}{Hot Tub Covers Canada}. Processing electronic payments, showcasing products, accessories, descriptions, managing reviews and comments.\\ %\textbf{Reference}: Jessica Dalen \ +1 (613) 421 2686\ \ $\cdotp$\ \ \href{mailto:jessica@dalendesign.ca}{jessica@dalendesign.ca}
}
\desc{\href{http://www.hegyigeomatics.com/}{Hegyi Geomatics international Inc}}{2009--2010}{\textbf{Software Developer} \\ Design and development of tools for a GIS framework related to the forest industry. In charge of creating Image analysis tools of forest stands using high resolution and Landsat imagery to monitor change, identify problems and perform forecasting. Analysis and visualizations were displayed on top of the NASA WorldWind 3D mapping application.
\\ 
%\textbf{Reference}: MSc.~Frank Hegyi \ +1 (613) 526 9967\ \ $\cdotp$\ \ \href{mailto:fhegyi@hegyigeomatics.com}{fhegyi@hegyigeomatics.com}
}

\desc{\href{http://www.eecs.uottawa.ca/}{University of Ottawa, Canada}}{2008--2010}{\textbf{Research Assistant, Computer Vision Software Developer}\\
Responsible for writing research papers, presenting research findings, and develop computer vision software to test and validate the results. Research on image processing techniques to extract relevant features from images. \\
	%  \textbf{Reference}: Prof.~Amiya Nayak \ $\cdotp$\ \  +1 (613) 562 5800x2165\ \ $\cdotp$\ \ \href{mailto: anayak@eecs.uottawa.ca}{anayak@eecs.uottawa.ca}
	  }
\desc{\href{http://www.navaera.com/web/form/home.faces}{Navaera USA LLC}}{2006--2008}{\textbf{Software Developer}\\ Creating a web crawler and multi-platform tools for automatic clustering of documents from the web based on their content and metadata (Java, C\#, and Python).\\
%\textbf{Reference}: Matthew Adler \ $\cdotp$\ \ \href{mailto: madler@navaera.com}{madler@navaera.com}
}

\desc{\href{http://www.uh.cu}{University of Havana, Cuba}}{2006--2008}{\textbf{Network Administrator, Software Developer} \\ 
IT Team leader for the main building of the University of Havana. Design, development, and validation of network administration tools for user monitoring, domain login, email access, and internet quota management. Provided network support and IT services. \\
%\textbf{Reference}: Sofia Sanju\'an G\'omez \ $\cdotp$\ \  +53 (7) 873 0123\ \ $\cdotp$\ \ \href{mailto: sanjuan@rect.uh.cu}{sanjuan@rect.uh.cu}
}


%----------------------------------------------------------------------------------------
%	EDUCATION
%--------------------------------------------------------------
\vspace{40pt}

\NewHeader{Education}

\desc{\href{http://www.eecs.uottawa.ca/}{University of Ottawa, Canada}}{2010-2016}{\textbf{Doctor of Philosophy in Computer Science} GPA: 10.0/10.0\\
Thesis: \textit{Efficient Feature extraction for Shape Analysis, Object Detection and Tracking}\newline
Robust feature representations to aid shape analysis, object detection and tracking.
\textbf{Supervisors}: Prof.~Jochen Lang \& Prof.~Robert Lagani\`ere}
\desc{\href{http://www.eecs.uottawa.ca/}{University of Ottawa, Canada}}{2009-2010}{\textbf{Master of Computer Science} GPA: 10.0/10.0 \\
Thesis: \textit{Towards Feature Detection based on Morphology of Objects on Images}\newline
Extracting lines and corners from images based on the morphology of objects.\newline
\textbf{Supervisor}: Prof.~Amiya Nayak}
\desc{\href{http://www.uh.cu}{University of Havana, Cuba}}{2001-2006}{\textbf{Bachelor of Computer Science} GPA: 4.56/5.0 (magna cum laude)\\Thesis: \textit{Diskless Cluster: Parallel and Distributed Systems}\newline
Bootable Cluster LiveCD based on Debian GNU/Linux distribution.\newline
\textbf{Supervisor}: Prof.~Joel de la Noval}

\newpage 

\NewHeader{Publications}

\desc{}{2016}{Matej Kristan, Andr\'es Sol\'is Montero et al. The Visual Object Tracking VOT2016 Challenge Results. \emph{The European Conference on Computer Vision (ECCV) Workshops}, Springer, 2016.}
\desc{}{2016}{Matej Kristan, Andr\'es Sol\'is Montero et al. The Thermal Infrared Visual Object Tracking VOT-TIR2016 Challenge Results. \emph{The European Conference on Computer Vision (ECCV) Workshops}, Springer, 2016.}

\desc{}{2015}{Andr\'es Sol\'is Montero, Jochen Lang, Robert Laganière. Scalable Kernel Correlation Filter With Sparse Feature Integration. \emph{The IEEE International Conference on Computer Vision (ICCV 2015), VOT Challenge}, pages 24-31, Dec. 2015.}

\desc{}{2015}{Matej Kristan, Andr\'es Sol\'is Montero et al. The Visual Object Tracking VOT2015 Challenge Results. \emph{The IEEE International Conference on Computer Vision (ICCV) Workshops}, pages 1-23, Dec. 2015.}



\desc{}{2015}{Michael Felsberg, Andr\'es Sol\'is Montero et al.  The Thermal Infrared Visual Object Tracking VOT-TIR2015 Challenge Results. \emph{The IEEE International Conference on Computer Vision (ICCV) Workshops}, pages 76-88, Dec. 2015.}

\desc{}{2015}{Andr\'es Sol\'is Montero, Jochen Lang, Robert Laganière. A General Framework for Fast 3D Object Detection and Localization Using an Uncalibrated Camera. \emph{IEEE Winter Conference on Applications of Computer Vision (WACV 2015)}, pages 884-891, Jan. 2015.}
\desc{}{2012}{Andr\'es Sol\'is Montero, Hicham Sekkati, Jochen Lang, Robert Laganière, Jeremy James. Framework for Natural Landmark-based Robot Localization. \emph{Proceedings of the 9th International Conference on Computer and Robot Vision (CRV)}, pages 131-138, April 2012. }
\desc{}{2012}{Andr\'es Sol\'is Montero, Jochen Lang. Skeleton pruning by
contour approximation and the integer medial axis
transform. \emph{Computers \& Graphics}, 36(5), pages 477-487, March 2012. }
\desc{}{2010}{Milos Stojmenovic, Andres Solis Montero, Amiya Nayak. Colour and texture based pyramidal image segmentation. \emph{IEEE International Conference on Audio Language and Image Processing (ICALIP)}, pages 778-786,  Nov. 2010. }
\desc{}{2010}{Andres Solis Montero, Milos Stojmenovic, Amiya Nayak.  Robust detection of corners and corner-line links in images. \emph{IEEE 10th International Conference on Computer and Information Technology (CIT)}, pages 495-502,  Jun. 2010. }
\desc{}{2010}{Milos Stojmenovic, Andres Solis Montero, Amiya Nayak.   Co-parent selection for fast region merging in pyramidal image segmentation. \emph{IEEE 2nd International Conference on Image Processing Theory Tools and Applications (IPTA)}, pages 243-248,  July 2010. }
\desc{}{2009}{Andres Solis Montero, Amiya Nayak, Milos Stojmenovic, Nejib Zaguia. Robust Line Extraction Based on Repeated Segment Directions on Image Contours. \emph{ IEEE Symposium: Computational Intelligence for Security and Defence Applications (CISDA)}, pages 1-7,  July 2009. }
\desc{}{2009}{Milos Stojmenovic, Andres Solis Montero, Amiya Nayak. Link Shifting Based Pyramid Segmentation for Elongated Regions.\emph{ Signal Processing, Image Processing and Pattern Recognition}, Springer Berlin Heidelberg, pages 141-152, 2009. }

\NewHeader{Licenses \& Certifications}

\desc{2022}{LF}
{\href{https://LF-dw7drkok9g}{Kubernetes Certified Application Developer (CKAD) } \hfill Cred ID: LF-dw7drkok9g \\
}
\desc{}{Udemy 2022}
{\href{https://ude.my/UC-525a18-34b-446d-800-26c3e7d97821}{Kubernetes Certified Application Developer (CKAD) } \hfill Cred ID: UC-5b25a18-34bf-446d-800f-26c3e7d97821 \\
}
\desc{2019}{Coursera}
{\href{https://www.coursera.org/account/accomplishments/specialization/G8YPRSBRUR4X}{Deep Learning Specialization} \hfill Cred ID: G8YPRSBRUR4X \\
 \href{https://www.coursera.org/account/accomplishments/verify/5D9RY2485Z4G}{Structuring Machine Learning Projects}
 	\hfill Cred ID: 5D9RY2485Z4G \\
 \href{https://www.coursera.org/account/accomplishments/verify/GCJHGKVL6ZLL}{Sequence Models}
 	\hfill Cred ID: GCJHGKVL6ZLL \\
 \href{https://www.coursera.org/account/accomplishments/verify/NQNLA6AYQ7NM}{ConvNN (i.e., LeNet, AlexNet,  GoogleNet, VGG, ResNets)}
 	\hfill Cred ID: NQNLA6AYQ7NM \\ 
 \href{https://www.coursera.org/account/accomplishments/verify/XJPXEXXMSB8K}{Neural Networks and Deep Learning}
 	\hfill Cred ID: XJPXEXXMSB8K \\ 
 \href{https://www.coursera.org/account/accomplishments/verify/XFSWVLMMR4KM}{Hyperparameter tuning, Regularization and Optimization}
 	\hfill Cred ID: XFSWVLMMR4KM \\
}


\NewHeader{Pattents}

\desc{\href{http://tempo-analytics.com/}{Tempo Analytics}}{2017}{System and method for gathering data related to quality of service in a customer service environment. CA 3014365 | PCT/CA2017/050849 | WO2019/010557.
}
\desc{}{}{}


\NewHeader{Teaching Experience}



\desc{\href{http://www.eecs.uottawa.ca/}{University of Ottawa}}{2009 -- 2015}{Programming Paradigms. (CSI2120), \hfill Winter $20\{15\mid11\}$.}
%\hfill Prof.  Amy Felty & Jochen Lang

%\hfill  Prof. Sherif G. Aly
\desc{}{}{Operative Systems (CSI 3131), \hfill Summer 2015.  }

% \hfill Prof.  Jochen Lang
\desc{}{}{Advanced Programming Concepts in C++\{11\} (CSI 2372). \hfill Fall $20\{14\mid12\mid10\}$.  }
%\hfill Prof.  Hussein Al Osman
%\desc{}{}{Introduction to Computing I (ITI 1120 - Java), \hfill Fall 2013. }

%\hfill Prof.  Vida Dujmovic
\desc{}{}{Introduction to Computing I \& II (ITI $11\{20\mid21\}$ - Python), \hfill Fall 2015.  }
%\hfill Prof.  Marcel Turcotte
\desc{}{}{Introduction to Computing I \& II (ITI $11\{20\mid21\}$ - Java), \hfill Winter $20\{14\mid13\}$. }

%\hfill Prof. Amiya Nayak
\desc{}{}{Computing Concepts for Business (CSI1306). \hfill Fall 2009. }
%\hfill   Prof. Luis Alberto Zarrabeitia

\desc{\href{http://www.uh.cu}{University of Havana}}{2006 -- 2008}{Network Administration in GNU/Linux, \hfill Fall $200\{7\mid8\}$ }
%\hfill  Prof.  Marta Montes de Oca
\desc{}{}{Object Oriented Programming with Java and C\#,   \hfill Summer $200\{8\mid7\}$.}
%\hfill  Prof.  Marta Montes de Oca
\desc{}{}{SQL and Relational Database Model Concepts, \hfill Fall 2005 }

% \hfill  Prof.  Julio Vidal
%\desc{}{}{Microsoft Office Tools (Word, Excel, Access), \hfill Summer 2006}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS
%----------------------------------------------------------------------------------------

\NewHeader{Skills \& Expertise}


\desc{}{Expertise}{Agile Management\ $\cdotp$\ Computer Vision\ $\cdotp$\ 
Image Processing\ $\cdotp$\  Machine Learning
Data Structure \& Algorithms\ $\cdotp$\ 
Object-Oriented Programming\ $\cdotp$\ 
RDMS (i.e., MSQL, MySQL, Postgres, and SQLite)\ $\cdotp$\ Non-SQL $\cdotp$\
Networking\ $\cdotp$\ Cloud Deployment $\cdotp$\ Containerization $\cdotp$\
Web Development/Design\ $\cdotp$\ 
e-Commerce\ $\cdotp$\ 
GIS\ $\cdotp$\ 
MVC}

\desc{}{Markup and Programming Languages}{C++\ $\cdotp$\ 
C\ $\cdotp$\ 
Python\ $\cdotp$\
Java\ $\cdotp$\ 
C\#\ $\cdotp$\ 
PHP\ $\cdotp$\ 
R\ $\cdotp$\
Matlab\ $\cdotp$\ 
JavaScript\ $\cdotp$\ 
Prolog\ $\cdotp$\ 
Perl\ $\cdotp$\ 
Bash\ $\cdotp$\ 
HTML 5\ $\cdotp$\ 
XML\ $\cdotp$\ 
CSS 3}

\desc{}{Software Development Tools}{OpenCV\ $\cdotp$\ 
 Microsoft Azure\ $\cdotp$\ 
 Kubernetes $\cdotp$\
 Docker $\cdotp$\
 Visual Studio\ $\cdotp$\ 
 Xcode\ $\cdotp$\
 Jupiter Labs\ $\cdotp$\ 
 Docker Images\ $\cdotp$\ 
 Git\ $\cdotp$\ 
 SVN\ $\cdotp$\ 
 make\ $\cdotp$\  
 jQuery\ $\cdotp$\ 
 \LaTeX\ $\cdotp$\  
 Adobe Photoshop\ $\cdotp$\  
 Adobe Illustrator\ $\cdotp$\ 
 Adobe Lightroom\ $\cdotp$\ 
 Adobe Dreamweaver\ $\cdotp$\ 
 OpenOffice\ $\cdotp$\  
 Microsoft Office Tools}

%------------------------------------------------

\newpage

\NewHeader{Honors \& Awards}

\desc{}{2022}{Award of Excellence: Innovation. Statistics Canada}
\desc{}{2020}{Outstanding Contribution Award. Statistics Canada}
\desc{}{2019}{Best Exterior Photo, First Place, Doors Opens/Portes Ouvertes by City of Ottawa}
\desc{}{2019}{Grand Prize Winner, Canada in One City Photo Contest by @Ottawatourism }
\desc{}{2019}{Grand Prize Photography Award, Ottawa in Bloom Contest by @Ottawatourism }

\desc{}{2018}{Professional Diploma in Photography (Shawacademy EQF Level 5). }
\desc{}{2016}{NSERC Engage Grant Program with Ross Video.}
\desc{}{2015}{Best real-time tracking method VOT Challenge 2015, Chile}
\desc{}{2015}{NSERC Engage Grant Program with Thales Canada.}
\desc{}{2014}{NSERC Engage Grant Program with You.i labs.}
\desc{}{2012}{NSERC Engage Grant Program with Cohort Systems Inc.}
\desc{}{2011}{NSERC CRD Grant with Pulse Microsystems Ltd.}
\desc{}{2010}{International Admission Scholarship from University of Ottawa.}



\desc{}{2010}{Ontario Centres of Excellence Grant with Hegyi Geomatics International Inc.\\
Project: “Green Earth (GIS)”.}
\desc{}{2009}{Excellence Scholarship from University of Ottawa.}
\desc{}{2009}{Ontario Centres of Excellence Grant with Hegyi Geomatics International Inc.\\
Project: “Green Earth (GIS)”.}
\desc{}{2009}{MITACS Accelerate Internship Program for graduate and postdoctoral fellows. \\ Project: “Advanced Tools for Forest Inventory and Management”.}
\desc{}{2006}{Magma cum laude graduate as Bachelor in Computer Science}



\NewHeader{Technical Reviews - Journals and Conferences}

\desc{}{}{IEEE Transactions on Instrumentation \& Measurement. $TIM\ 20\{16\mid17\mid18\}$.}
\desc{}{}{IEEE  Transactions on Image Processing. $TIP \ 2015$.}
\desc{}{}{IEEE International Conference on Multimedia and Expo. $ICME\ 2013$.}
\desc{}{}{IEEE International Conference on Robotics and Automation. $ICRA\ 2013$.} 
\desc{}{}{IEEE International Conference on Multimedia and Expo. $ICME\ 2012$.}
\desc{}{}{IEEE International Conference on Multimedia and Expo. $ICME\ 2011$.}
\desc{}{}{7th IEEE International Conference on Mobile Ad-hoc and Sensor Systems. $MASS\ 2010$.}

\newpage
\NewHeader{Additional Information}


\desc{}{Citizenship}{\lang{Canadian}}
\desc{}{Languages}{\lang{English}\ : \ Fluent\\ \lang{Spanish}\ : \ Native\\ \lang{French}\ : \ Beginner}



\desc{}{Security Clearance}{{\color{maroon(html/css)}\textsc{Reliability}} : expiring 2027 \ \  $\cdotp$ \ \ 
	{{\color{maroon(html/css)}\textsc{Secret}} : expiring 2028 }}


\desc{}{Affiliations}{ACM member \ $\cdotp$\  IEEE member \ $\cdotp$\  International High IQ Society member}

\desc{}{Interests \& Hobbies}{Photography (IG: @asolism) \ \ $\cdotp$\ \ Motorcycle Riding\ \ $\cdotp$\ \ Dancing\ \ $\cdotp$\ \ Music\ \ $\cdotp$\ \ Soccer\ \ $\cdotp$\ \ Volleyball\ \ $\cdotp$\ \ Skating\ \ $\cdotp$\ \ Baseball \ \ $\cdotp$\ \ Cross-country skiing \ \ $\cdotp$\ \ Discovering new places and restaurants }
\end{cv}



\end{document}
